Columnar VCF using Zarr

### 2024-03-12 paper.tex
Remove supplemental plot

\clearpage
\renewcommand\thefigure{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand\thetable{S\arabic{table}}
\setcounter{table}{0}

\section*{Supplementary Material}

\begin{figure*}[ht]
	\begin{center}
		\includegraphics[width=\textwidth]{figures/whole-matrix-compute-supplemental}
	\end{center}
	\caption{\label{fig-whole-matrix-compute-supplemental}
    Limitations of vertical scaling on whole-matrix afdist. The elapsed
wall-clock time required to compute afdist on the whole genotype matrix using
different numbers of threads and storage backends (top row), and the relative
speedup obtained from threads as a fraction of optimum speedup (bottom row).
[TODO more detail and link to fig 1. Also add the times for bcftools and
genozip in col 1?]
}
\end{figure*}

>>>>

% \clearpage
% \renewcommand\thefigure{S\arabic{figure}}
% \setcounter{figure}{0}
% \renewcommand\thetable{S\arabic{table}}
% \setcounter{table}{0}

% \section*{Supplementary Material}

% \begin{figure*}[ht]
% 	\begin{center}
% 		\includegraphics[width=\textwidth]{figures/whole-matrix-compute-supplemental}
% 	\end{center}
% 	\caption{\label{fig-whole-matrix-compute-supplemental}
%     Limitations of vertical scaling on whole-matrix afdist. The elapsed
% wall-clock time required to compute afdist on the whole genotype matrix using
% different numbers of threads and storage backends (top row), and the relative
% speedup obtained from threads as a fraction of optimum speedup (bottom row).
% [TODO more detail and link to fig 1. Also add the times for bcftools and
% genozip in col 1?]
% }
% \end{figure*}
